Equilibria and Convergence of Fictitious Play on Network Aggregative Games

### 2021-05-27 Documents/FP in NAGs/neurips_2021.tex
Updated Experiment Figures

  \begin{figure}[t]
    \centering
    \begin{subfigure}[b]{0.45 \textwidth}
      \includegraphics[width = 0.8\textwidth]{Figures/convergentShapley.png}
    \caption{\label{fig::convergentShapley}}
    \end{subfigure}
    \begin{subfigure}[b]{0.45 \textwidth}
      \includegraphics[width = 0.8 \textwidth]{Figures/nonConvergentShapley.png}
      \caption{\label{fig::nonconvergentShapley}}
    \end{subfigure}
    \caption{\label{fig::Shapley} Orbits of the Fictitious Play in the Three Player Chain (c.f.
    Figure \ref{fig::ThreePlayerNetwork}) with payoff matrices given by (a)
    (\ref{eq::zeroSumShapley}) showing convergence to the interior NE (b)
    (\ref{eq::nonzeroSumShapley}) showing cycles around the interior NE.}
  \end{figure}

>>>>

  \begin{figure}[t]
    \centering
    \begin{subfigure}[b]{0.45 \textwidth}
      \includegraphics[width = 0.8\textwidth]{Figures/convergentShapley.png}
    \caption{\label{fig::convergentShapley}}
    \end{subfigure}
    \begin{subfigure}[b]{0.45 \textwidth}
      \includegraphics[width = 0.8 \textwidth]{Figures/nonConvergentShapley.png}
      \caption{\label{fig::nonconvergentShapley}}
    \end{subfigure}
    \caption{\label{fig::Shapley} Orbits of the Fictitious Play in the Three Player Chain for which the NE lies at the centre of the simplex. (a) Payoffs are given by
    (\ref{eq::zeroSumShapley}). The plot shows NA-CTFP yields convergence to the NE (b)
	NA-CTFP showing cycles around the NE when payoffs are modified slightly (c.f. Sec.~\ref{sec::NonConv}).}
  \end{figure}
